A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-07-29 sections/04-researchdesign.tex
Re-defining initial research questions
Add figures to text, start to compose the section

>>>>

\begin{description}
\item[RQ1:] \textit{Which API is easier to learn and use according to the student perceptions?}
%
...
\item[RQ2:] \textit{Which API is better to improve the performance according to the student perceptions?}
%
...

\end{description}

\subsection{Student Background}

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.85\columnwidth]{background_mean_knowledge}
    \caption{Student mean knowledge \textit{before} the assignment}
    \label{fig:student-mean-knowledge}
\end{figure}

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.85\columnwidth]{yes_no_questions}
    \caption{Student API knowledge \textit{before} the assignment and their relation to classes}
    \label{fig:student-knowledge-yes-no}
\end{figure}
